Check Coverage

### 2020-03-05 analysis/merge_data.Rmd
Make glm correction a function.

First for one study, 311
```{r}
model_data <- fd_table %>% filter(metric == "FRic", study_id == 311)
fit <- glm(value ~ year + richness, data = model_data)

pred_vars <- model_data %>% 
  select(richness, year) %>% 
  distinct() %>%
  mutate(fric_pred = predict(fit, ., type = "response"))

@@

>>>>

First for one study, 311
```{r}

glm_correction <- function(study, plot_num){
  model_data <- fd_table %>% filter(metric == "FRic", study_id == study, plot == plot_num)
  fit <- glm(value ~ richness, data = model_data)

  pred_vars <- model_data %>% 
    select(richness) %>% 
    distinct() %>%
    mutate(fric_pred = predict(fit, ., type = "response"))

@@

  return(plot_data)
}

plot_data <- glm_correction(311, 1)
